---
title: "Assignment_2_map"
author: "Sam Zbib"
date: "March 4, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.


## Assignment 2  - Peer reviewed


### Display Date as of today - 60 days (two months back) 


### Display an interactive map with a popup for my home address.


##  Code to setup the library and intialize the map 

```{r, echo = TRUE  }
library (leaflet)

my_map <- leaflet() %>%
   addTiles ()
```


## code to add a pop up for my home address and a time stamp for 60 days ago


```{r, echo = TRUE  }
my_map <- my_map  %>%
    addMarkers(lat=34.052464, lng= -84.239713, popup="Sam Zbib's Home") %>%
   addControl ( html = format (Sys.Date()-60,"%A, %b %d %Y"))


```

## Interactive  Map with Date timestamp 


``` {r, echo = FALSE  }

my_map

```

