---
title: "First Presentation"
author: "Sam Zbib"
date: "March 2, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```
## A new Slide without Content 

- Bullet Item 1 
- Bullet Item 2 
...
1. Item a  
2. Item b 


*Italicised Text *

**Bold Text ** 

`for (i %in% 1:10)'

## **Cars slide ** 

``` {r, comment = "", echo = TRUE, eval = TRUE, fig.align = 'center', fig.cap = 'MT Cars plot' }
plot (mtcars$wt, mtcars$mpg, xlab =  "Weight", ylab = "MPG" )
```

## Another Slide
### Top Level Headiing
#### Subheading 1 
#### Subheading 2 

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

